Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-16 paper/us_election_2020.qmd
render paper

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check
In @fig-post_dist, we implement a posterior distribution. This compares who people voted for in reality with the prediction results from the posterior distribution from our logistic regression model. It can be observed that the posterior distribution fits perfectly with the actual data, it suggests that the model accurately captures the observed data patterns. So the posterior is able to generate simulated data that closely resembles the actual data [@bayes_post]. This is a positive sign because it indicates that our logistic regression model is a good representation of the actual voting preferences in the 2020 election data.

@@

posterior_vs_prior(political_preferences1) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Credibility Interval {#sec-credibility-interval}

## Markov chain Monte Carlo Convergence Check

@@

>>>>

## Model details {#sec-model-details}

### Posterior predictive check
In @fig-post_dist, we implement a posterior distribution. This compares who people voted for in reality with the prediction results from the posterior distribution from our logistic regression model. It can be observed that the posterior distribution fits perfectly with the actual data, it suggests that the model accurately captures the observed data patterns. So the posterior is able to generate simulated data that closely resembles the actual data [@bayes_post]. This is a positive sign because it indicates that our logistic regression model is a good representation of the actual voting preferences in the 2020 election data.

@@

posterior_vs_prior(political_preferences1, size = 0.3) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  coord_flip()
```

### Markov chain Monte Carlo Convergence Check

@@

### Credibility Interval {#sec-credibility-interval}
90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
